% TC-0014 fragment; included by c89-test-report.tex.
\def\TCID{TC-0014}
\def\TCTitle{C89 byte and string handling}
\def\TCPurpose{Verify all 22 functions across overlap, boundaries, high-bit
bytes, searches, C-locale collation, token state, and error messages.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0014}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.11.}
\def\TCFeatureRef{\texttt{include/string.h}; \texttt{src/string.c};
\texttt{tests/c89/string.c}; \texttt{tests/c89/run-tc-0014.ps1}.}
\def\TCPreconditions{TinyCC and the WCRT errno implementation are available.}
\def\TCEnvironment{Behavioral execution on x64 plus Windows ARM64 cross-build;
comparison execution uses Microsoft UCRT.}
\def\TCAssumptions{The active collation locale is the mandatory C locale and
\texttt{strtok} is intentionally non-reentrant.}
\def\TCInputData{Zero lengths, overlapping regions, padded buffers, high-bit
bytes, empty strings, delimiters, terminators, and error numbers.}
\def\TCInitialState{The token continuation pointer has no active sequence.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile the declaration-presence source without host headers.
\item Execute copying, comparison, search, transform, token, and error checks.
\item Cross-link the same implementation as PE/COFF ARM64.
\end{enumerate}}
\def\TCExpectedResult{All 22 functions meet their tested C89 boundary and
return-value contracts on x64 and cross-build cleanly for ARM64.}
\def\TCPostConditions{Only static \texttt{strtok} continuation state may have
changed.}
\TCTemplate
