% TC-0009 fragment; included by c89-test-report.tex.
\def\TCID{TC-0009}
\def\TCTitle{C89 signal handling}
\def\TCPurpose{Verify declarations, disposition changes, synchronous delivery,
handler reset, ignored signals, invalid requests, and default termination.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0009}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.7, 4.7.1.1, and 4.7.2.1.}
\def\TCFeatureRef{\texttt{include/signal.h}; \texttt{src/signal.c};\par
\texttt{src/platform/windows/signal.c}; \texttt{tests/c89/signal.c};\par
\texttt{tests/c89/signal\_default.c};
\texttt{tests/c89/run-tc-0009.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers
exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation and behavioral execution against
WCRT and Microsoft UCRT.}
\def\TCAssumptions{Delivery is synchronous; Windows events and exceptions are
not automatically translated.}
\def\TCInputData{Six signal numbers, three standard dispositions, a user
handler, and an unsupported signal number.}
\def\TCInitialState{Every supported signal has its default disposition.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/signal.c} as C89 without linking.
\item Register and replace a handler for every supported signal.
\item Raise each signal and verify delivery, reset, and ignore behavior.
\item Verify invalid requests fail without changing valid state.
\item Run the WCRT default action in a child and verify exit code 143.
\end{enumerate}}
\def\TCExpectedResult{Both targets pass safe behavior; WCRT also proves
deterministic default termination in a child process.}
\def\TCPostConditions{Generated objects, executables, and evidence remain under
ignored output directories.}
\TCTemplate
