% TC-0008 fragment; included by c89-test-report.tex.
\def\TCID{TC-0008}
\def\TCTitle{C89 non-local jumps}
\def\TCPurpose{Verify saved contexts, direct and resumed values, stack restoration, nested environments, and volatile state.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0008}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.6, 4.6.1.1, and 4.6.2.1.}
\def\TCFeatureRef{\texttt{include/setjmp.h};\par
\texttt{src/platform/windows/setjmp.S};\par
\texttt{tests/c89/setjmp.c}; \texttt{tests/c89/run-tc-0008.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation and behavioral execution against WCRT assembly and Microsoft UCRT.}
\def\TCAssumptions{Tests use live same-thread contexts and do not depend on modified nonvolatile automatic objects.}
\def\TCInputData{Zero and nonzero values, nested contexts, an additional stack frame, and a volatile object.}
\def\TCInitialState{The jump buffer contains no saved environment.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/setjmp.c} as C89 without linking.
\item Build and execute \texttt{tests/c89/setjmp.c} against both targets.
\item Verify values, zero conversion, nesting, stack restoration, and volatile state.
\end{enumerate}}
\def\TCExpectedResult{Both targets complete every defined-lifetime non-local control-flow check.}
\def\TCPostConditions{Generated objects, executables, and evidence remain under ignored output directories.}
\TCTemplate
