% TC-0003 fragment; included by c89-test-report.tex.
\def\TCID{TC-0003}
\def\TCTitle{C89 error indicator}
\def\TCPurpose{Verify that \texttt{errno.h} supplies distinct positive error constants and stable, non-aliasing, modifiable \texttt{errno} storage.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0003}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.1.3.}
\def\TCFeatureRef{\texttt{include/errno.h}; \texttt{src/errno.c};\par
\texttt{tests/c89/presence/errno.c}; \texttt{tests/c89/errno.c};\par
\texttt{tests/c89/run-tc-0003.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation and behavioral execution against WCRT and Microsoft UCRT.}
\def\TCAssumptions{WCRT uses process-global storage until a later threading requirement changes only its backing expression.}
\def\TCInputData{Both error constants, repeated assignments, address expressions, and an unrelated object.}
\def\TCInitialState{No runtime error state is required.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/errno.c} as C89 without linking.
\item Build and run \texttt{tests/c89/errno.c} against WCRT and UCRT.
\item Verify positive distinct constants, assignment, stable address, and non-aliasing storage.
\end{enumerate}}
\def\TCExpectedResult{Both targets pass every constant and storage check. Math and conversion producer checks execute with their owning requirements.}
\def\TCPostConditions{Generated objects, executables, and evidence remain under ignored output directories.}
\TCTemplate
