% TC-0013 fragment; included by c89-test-report.tex.
\def\TCID{TC-0013}
\def\TCTitle{C89 general utilities}
\def\TCPurpose{Verify all 29 conversion, random, allocation, process,
algorithm, arithmetic, and C-locale multibyte functions.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0013}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.10.}
\def\TCFeatureRef{\texttt{include/stdlib.h}; \texttt{src/stdlib.c};\par
\texttt{src/platform/windows/heap.c};
\texttt{src/platform/windows/process.c};\par
\texttt{tests/c89/stdlib.c}; \texttt{tests/c89/stdlib\_exit.c}.}
\def\TCPreconditions{TinyCC and the WCRT ctype, errno, and string facilities
are available.}
\def\TCEnvironment{x64 behavioral execution, child-process termination proof,
Microsoft UCRT comparison, and Windows ARM64 cross-build.}
\def\TCAssumptions{Multibyte conversion uses the mandatory single-byte C
locale. Zero-size allocation returns a freeable unique allocation.}
\def\TCInputData{Signed, based, decimal, and overflowing conversions; heap
sizes; arrays; division; environment names; and multibyte strings.}
\def\TCInitialState{Random state is implementation-defined and no exit
callbacks are registered.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile the presence source without host standard headers.
\item Execute conversions, allocation, algorithm, and multibyte checks.
\item Run reverse-order exit callbacks in a child and require status 23.
\item Cross-link the implementation as PE/COFF ARM64.
\end{enumerate}}
\def\TCExpectedResult{Every function meets its tested C89 contract, the child
exits with status 23, and the ARM64 artifact has machine type AA64.}
\def\TCPostConditions{All test allocations are freed and child state is
discarded at process termination.}
\TCTemplate
