% TC-0012 fragment; included by c89-test-report.tex.
\def\TCID{TC-0012}
\def\TCTitle{C89 input and output}
\def\TCPurpose{Verify all 41 functions across files, temporary streams,
text translation, positioning, indicators, formatting, and scanning.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0012}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.9.}
\def\TCFeatureRef{\texttt{include/stdio.h}; \texttt{src/stdio.c};
\texttt{src/stdio\_format.c}; \texttt{src/stdio\_scan.c};\par
\texttt{src/platform/windows/file.c}; \texttt{tests/c89/stdio.c}.}
\def\TCPreconditions{TinyCC and WCRT ctype, errno, string, and stdlib are
available.}
\def\TCEnvironment{x64 behavioral execution and Windows ARM64 cross-build.
Current Microsoft UCRT headers omit the removed C89 \texttt{gets} declaration.}
\def\TCAssumptions{Tests use bounded records and do not call unsafe
\texttt{gets}.}
\def\TCInputData{Text and binary files, temporary names, CR-LF, pushed-back
bytes, all conversion families, widths, precision, modifiers, and scansets.}
\def\TCInitialState{No dynamic WCRT stream slot is open.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile all required declarations without host standard headers.
\item Exercise file lifecycle, direct I/O, positioning, and indicators.
\item Exercise formatted output, input, suppression, scansets, and counts.
\item Cross-link the complete subsystem as PE/COFF ARM64.
\end{enumerate}}
\def\TCExpectedResult{All 41 WCRT functions pass behavioral checks and the
complete subsystem cross-builds with ARM64 machine type AA64.}
\def\TCPostConditions{All test streams close and named test files are removed.}
\TCTemplate
