% TC-0002 fragment; included by c89-test-report.tex.
\def\TCID{TC-0002}
\def\TCTitle{C89 character handling}
\def\TCPurpose{Verify the complete C89 character-classification and case-mapping API over \texttt{EOF} and the full unsigned-character domain.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0002}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.3, 4.3.1, and 4.3.2.}
\def\TCFeatureRef{\texttt{include/ctype.h}; \texttt{src/ctype.c};\par
\texttt{tests/c89/presence/ctype.c}; \texttt{tests/c89/ctype.c};\par
\texttt{tests/c89/run-tc-0002.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation plus behavioral execution against WCRT with TinyCC and against Microsoft UCRT with MSVC.}
\def\TCAssumptions{WCRT currently supports only the required \texttt{C} locale; function forms guarantee single evaluation.}
\def\TCInputData{Typed references to all 13 functions, \texttt{EOF}, and every integer from 0 through 255.}
\def\TCInitialState{No locale or runtime state is required.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/ctype.c} as C89 without linking.
\item Build \texttt{tests/c89/ctype.c} against WCRT and Microsoft UCRT.
\item Execute classification and case-mapping checks for \texttt{EOF} and every value from 0 through 255.
\item Verify required class relationships and unchanged unmapped values.
\end{enumerate}}
\def\TCExpectedResult{Both targets expose all 13 addressable functions and produce the required \texttt{C}-locale result for every tested input.}
\def\TCPostConditions{Generated executables and objects remain under ignored build and evidence directories.}
\TCTemplate
