% TC-0007 fragment; included by c89-test-report.tex.
\def\TCID{TC-0007}
\def\TCTitle{C89 mathematics}
\def\TCPurpose{Verify all 22 C89 mathematics functions, numerical identities, quadrants, output pointers, and error behavior.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0007}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.5 through 4.5.6.}
\def\TCFeatureRef{\texttt{include/math.h}; \texttt{src/math.c};\par
\texttt{tests/c89/presence/math.c}; \texttt{tests/c89/math.c};\par
\texttt{tests/c89/run-tc-0007.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation and behavioral execution against WCRT and Microsoft UCRT.}
\def\TCAssumptions{Tests use finite binary64 inputs and scaled tolerances from \texttt{1e-12} through \texttt{1e-10}.}
\def\TCInputData{Ordinary values, identities, all quadrants, pointer outputs, domain errors, range errors, and \texttt{HUGE\_VAL}.}
\def\TCInitialState{No floating environment or \texttt{errno} state is required.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/math.c} as C89 without linking.
\item Build and execute \texttt{tests/c89/math.c} against both targets.
\item Verify numerical values, identities, quadrants, output pointers, and rounding functions.
\item Provoke domain and range errors and verify the C89 error indicator.
\end{enumerate}}
\def\TCExpectedResult{WCRT passes all 35 checks without host math delegation. Target differences remain explicit in comparison evidence.}
\def\TCPostConditions{Generated objects, executables, and evidence remain under ignored output directories.}
\TCTemplate
