% TC-0004 fragment; included by c89-test-report.tex.
\def\TCID{TC-0004}
\def\TCTitle{C89 floating-point limits}
\def\TCPurpose{Verify every C89 floating-point model and limit macro and its consistency with stored arithmetic behavior.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0004}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.1.4.}
\def\TCFeatureRef{\texttt{include/float.h};\par
\texttt{tests/c89/presence/float.c}; \texttt{tests/c89/float.c};\par
\texttt{tests/c89/run-tc-0004.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation and stored arithmetic execution against WCRT and Microsoft UCRT.}
\def\TCAssumptions{Volatile objects force values through the target storage format before epsilon comparisons.}
\def\TCInputData{All required model and limit macros plus stored values at one and one epsilon above one.}
\def\TCInitialState{No floating-point environment state is required.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/float.c} as C89 without linking.
\item Build and execute \texttt{tests/c89/float.c} against both targets.
\item Verify environmental minima, ordering, ranges, exponents, and stored epsilon behavior.
\end{enumerate}}
\def\TCExpectedResult{Every macro is present and both target models satisfy all representation and arithmetic checks.}
\def\TCPostConditions{Generated objects, executables, and evidence remain under ignored output directories.}
\TCTemplate
