% TC-0006 fragment; included by c89-test-report.tex.
\def\TCID{TC-0006}
\def\TCTitle{C89 localization}
\def\TCPurpose{Verify C89 locale selection, queries, failure behavior, convention data, and character-classification interaction.}
\def\TCPriority{\TCPriorityHigh}
\def\TCRequirementRef{REQ-0006}
\def\TCDesignRef{ANSI X3J11 C89 draft 4.4, 4.4.1, and 4.4.2.}
\def\TCFeatureRef{\texttt{include/locale.h}; \texttt{src/locale.c};\par
\texttt{src/internal/locale.h}; \texttt{tests/c89/locale.c};\par
\texttt{tests/c89/run-tc-0006.ps1}.}
\def\TCPreconditions{TinyCC is available in \texttt{PATH}; WCRT public headers exist under \texttt{include}.}
\def\TCEnvironment{C89 presence compilation and behavioral execution against WCRT and Microsoft UCRT.}
\def\TCAssumptions{The mandatory \texttt{C} locale is WCRT's only currently supported locale.}
\def\TCInputData{All categories, queries, \texttt{C}, invalid requests, every convention member, and representative ctype input.}
\def\TCInitialState{No active locale state is required.}
\def\TCProcedure{\par\begin{enumerate}
\item Compile \texttt{tests/c89/presence/locale.c} as C89 without linking.
\item Build and execute \texttt{tests/c89/locale.c} against both targets.
\item Verify startup, categories, queries, invalid requests, conventions, and ctype behavior.
\end{enumerate}}
\def\TCExpectedResult{Both targets expose the complete API and satisfy all mandatory \texttt{C}-locale checks.}
\def\TCPostConditions{Generated objects, executables, and evidence remain under ignored output directories.}
\TCTemplate
